---
title: "NBA 2014-2015球季 各隊分析"
author: "B0244213"
date: "2016年3月26日"
output: ioslides_presentation
---
#NBA 2014-2015球季 各隊分析

##把NBA14-15的資料讀進來
```{r results='hide',message=FALSE,cache=T}
if (!require('SportsAnalytics')){
    install.packages("SportsAnalytics")
    library(SportsAnalytics)
}
NBA1415<-fetch_NBAPlayerStatistics("14-15")
NBA1415
install.packages("data.table")
library(data.table)

##各隊最辛苦的球員
```{r}
MaxPlayed<-aggregate(TotalMinutesPlayed~Team,NBA1415,max)
#tapply(NBA1415$TotalMinutesPlayed,NBA1415$Team,max)
NBA1415MaxPlayed<-merge(NBA1415,MaxPlayed)
output<-NBA1415MaxPlayed[order(NBA1415MaxPlayed$TotalMinutesPlayed,decreasing = T),c("Team","Name","TotalMinutesPlayed")]
library(knitr)
kable(output, digits=2)

##各隊得分王
```{r}
MaxPoint<-aggregate(TotalPoints~Team,NBA1415,max)
#tapply(NBA1415$TotalPoints,NBA1415$Team,max)
NBA1415MaxPoint<-merge(NBA1415,MaxPoint)
output<-NBA1415MaxPoint[order(NBA1415MaxPoint$TotalPoints,decreasing = T),c("Team","Name","TotalPoints")]
library(knitr)
kable(output, digits=2)

##各隊最有效率的球員
```{r}
NBA1415DT<-data.table(NBA1415)
output<-NBA1415DT[,list(Efficiency=round(sum(TotalPoints)/sum(TotalMinutesPlayed),digits = 2)),
          by=list(Team,Name)] [order(Efficiency,decreasing = T)]
library(knitr)
kable(output, digits=2)

##各隊三分球出手最準的球員
```{r}
NBA1415DT<-data.table(NBA1415)
output<-NBA1415DT[,list(ThreePerc=round(sum(ThreesMade)/sum(ThreesAttempted),digits = 2)),
          by=list(Team,Name)] [order(ThreePerc,decreasing = T)]
library(knitr)
kable(output, digits=2)
